Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-05-10 main.tex
Updates from Overleaf

%Director,
$^{2}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip, 
    Taipei Municipal Wanfang Hospital\unskip, Taipei\unskip, Taiwan\\

$^{3}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip,
    Taipei Medical University Hospital\unskip, Taipei\unskip, Taiwan\\

$^{4}$ \quad Genomics Research Center\unskip, 
    Academia Sinica\unskip, Taipei\unskip, Taiwan\\
$^{5}$ \quad Graduate Institute of Biomedical Informatics, College of Medical Science and Technology\unskip, Taipei Medical University\unskip, Taipei\unskip, Taiwan\\
}

>>>>

%Director,
$^{2}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip, 
%    Taipei Municipal Wanfang Hospital\unskip, Taipei\unskip, Taiwan\\
Wan Fang Hospital\unskip, Taipei Medical University\\

$^{3}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip,
    Taipei Medical University Hospital\unskip, Taipei Medical University\\

$^{4}$ \quad Genomics Research Center\unskip, 
    Academia Sinica\unskip, Taipei\unskip, Taiwan\\

$^{5}$ \quad Graduate Institute of Biomedical Informatics, College of Medical Science and Technology\unskip, Taipei Medical University\unskip,
No.172-1, Sec. 2, Keelung Rd.\unskip, Taipei 106\unskip, Taiwan\\
%Taipei\unskip, Taiwan\\
}
